Reduced plasticity and relative variance in physiological rates of ectotherm populations under climate change

### 2024-06-24 ms.qmd
Updated pub bias. Use of effective sample size, rerun models controlling for max temp, better reporting in supplement and better description in methods

We explored the possibility for publication bias graphically using funnel plots, and more formally by including sampling variance (or sampling standard error) in our meta-regression models  [@Nakagawa2022-gy]. Funnel plot asymmetry may suggest a form of publication bias called the 'file-drawer' effect whereby low-powered studies are less likely to be published. To test whether sampling variance covaried with effect size we included it in a multi-level meta-regression model that accounted for all the random effects (study, species, trait) and fixed effects (acclimation time, type of effect, habitat, trait category and the interaction between habitat type and trait category).

@@

Funnel plots did not show any noticeable deviation from the typical funnel shape for any of the effect size estimates (@fig-s2).

```{r, pubias}
#| label: pubias
#| echo: false
#| include: false
rerun = FALSE
if(rerun){
  model_full_lnrr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + V + habitat*life.hist*type + trait_category + habitat:type + habitat:life.hist + habitat:life.hist:type + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c | spp) + (1 | trait) + (1  | obs),  data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)

  model_full_lncvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~ max_temp_c +  c_accl_time + V + habitat*life.hist*type + trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1 | trait) + (1  | obs),  data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data)

  model_full_lnvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + V + habitat*life.hist*type + trait_category  + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 + max_temp_c | spp) + (1 | trait) + (1  | obs),  data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnVRQ10_data)

@@

>>>>

We explored the possibility for publication bias graphically using funnel plots, and more formally by including the square root of the inverse effective sample size ($\sqrt{1/ne}$) in our meta-regression models  [@Nakagawa2022-gy]. Funnel plot asymmetry may suggest a form of publication bias called the 'file-drawer' effect whereby low-powered studies are less likely to be published, however, graphical approaches do not account for sources of non-independence and high heterogeneity which can drive apparent funnel asymmetry [@Nakagawa2022-gy]. As such, we included $\sqrt{1/ne}$ as a moderator in a multi-level meta-regression model that accounted for all the random effects (i.e, study, species, trait) and fixed effects (acclimation time, type of effect, habitat, trait category and the interaction between habitat type and trait category). While sampling standard error (or variance) could have been included in our model, @Nakagawa2022-gy suggested instead to use $\sqrt{1/ne}$ (and its square root) to avoid potential problems with using sampling error itself (see @Nakagawa2022-gy for a discussion).

@@

```{r, pubias}
#| label: pubias
#| echo: false
#| include: false
rerun = FALSE
if(rerun){

# USe effective sample size instead because sampling variance estimates could indue a spurious correlation with our effect size
    lnRRQ10_data <- lnRRQ10_data %>%  
              mutate(n_ef = ifelse(name == "lnRR_Q10_acute_t1", (4*r1.1_N*r1.2_N)/(r1.1_N + r1.2_N), # acute 1
                            ifelse(name == "lnRR_Q10_acute_t2", (4*r2.1_N*r2.2_N)/(r2.1_N + r2.2_N), # acute 2
                                                                (4*r1.1_N*r2.2_N)/(r1.1_N + r2.2_N)))) # acclimation

    lnCVRQ10_data <- lnCVRQ10_data %>%  
              mutate(n_ef = ifelse(name == "lnCVR_Q10_acute_t1", (4*r1.1_N*r1.2_N)/(r1.1_N + r1.2_N), # acute 1
                            ifelse(name == "lnCVR_Q10_acute_t2", (4*r2.1_N*r2.2_N)/(r2.1_N + r2.2_N), # acute 2
                                                                (4*r1.1_N*r2.2_N)/(r1.1_N + r2.2_N)))) # acclimation

    lnVRQ10_data <- lnVRQ10_data %>%  
              mutate(n_ef = ifelse(name == "lnVR_Q10_acute_t1", (4*r1.1_N*r1.2_N)/(r1.1_N + r1.2_N), # acute 1
                            ifelse(name == "lnVR_Q10_acute_t2", (4*r2.1_N*r2.2_N)/(r2.1_N + r2.2_N), # acute 2
                                                                (4*r1.1_N*r2.2_N)/(r1.1_N + r2.2_N)))) # acclimation

  model_full_lnrr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + sqrt(1/n_ef) + habitat*life.hist*type + trait_category + habitat:type + habitat:life.hist + habitat:life.hist:type + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 + max_temp_c | spp) + (1 | trait) + (1  | obs),  data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data)

  #Pull the posterior for the slope with sqrt effective n
  post_pb_lnrr <- posterior_samples(model_full_lnrr_pb, "^b_sqrt1Dn_ef")[,1]

  model_full_lncvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~ max_temp_c +  c_accl_time + sqrt(1/n_ef) + habitat*life.hist*type + trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 + max_temp_c| spp) + (1 | trait) + (1  | obs),  data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnCVRQ10_data)

  #Pull the posterior for the slope with sqrt effective n
  post_pb_lncvr <- posterior_samples(model_full_lncvr_pb, "^b_sqrt1Dn_ef")[,1]

  model_full_lnvr_pb <- brms::brm(effect_size | se(sqrt(V)) ~  max_temp_c + c_accl_time + sqrt(1/n_ef) + habitat*life.hist*type + trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_VR)) + (1 + max_temp_c | spp) + (1 | trait) + (1  | obs),  data2 = list(A_VR=A_VR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnVRQ10_data)

  #Pull the posterior for the slope with sqrt effective n
  model_full_lnvr_pb <- posterior_samples(model_full_lnvr_pb, "^b_sqrt1Dn_ef")[,1]

@@

Funnel plots did not show any noticeable deviation from the typical funnel shape for any of the effect size estimates (@fig-s2). Meta-regression models including sampling standard error as a moderator also suggested no relationship with effect size for $lnRR_{Q_{10}}$ ($\beta$ = `r mean(post_pb_lnrr)`, 95% CI: `r quantile(post_pb_lnrr, 0.025)` to `r quantile(post_pb_lnrr, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(post_pb_lnrr))`), $lnCVR_{Q_{10}}$ ($\beta$ = `r mean(post_pb_lncvr)`, 95% CI: `r quantile(post_pb_lncvr, 0.025)` to `r quantile(post_pb_lncvr, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(post_pb_lncvr))`) or $lnVR_{Q_{10}}$ ($\beta$ = `r mean(model_full_lnvr_pb)`, 95% CI: `r quantile(model_full_lnvr_pb, 0.025)` to `r quantile(model_full_lnvr_pb, 0.975)`, $p_{MCMC}$ = `r p_value(pmcmc(model_full_lnvr_pb))`) was not significant indicating little evidence for publication bias.
